\thispagestyle{empty}
\vspace*{3cm}
\begin{center}
    \textbf{Acknowledgement}
\end{center}

% todo : Writing Acknoeledgement
\noindent
First of all, I would like to thank Prof. Dr. Klaus-Robert M\"{u}ller and Dr. Gr\'{e}goire Montavon for this research opportunity, invaluable guidance throughout  the course of conducting the thesis and facilitating me at TU Berlin, Machine Learning group with a great research atmosphere.
\\

\noindent
Secondly, I would also like to thank Prof. Dr. Klaus Obermayer and his staffs at Neural Information Processing group for organizing Machine Intelligence I \& II and Neural Information Project course. These courses provided me necessary knowledge to conduct this thesis.
\\

\noindent
Importantly, I would like to special thank to my family for always supporting me. These people always encourage me to develop and pursue my own interests.
\\

\noindent
I would like to say thank you to my all friends for all discussion we had, especially EIT Data Science fellows including Akash Singh, Zitong Lian, Pham Duy and Shashank Srivastava who gave me detailed feedback of the first draft of this thesis. I would also like to thank EIT Master School, TU/e and TUB staffs who have been organizing this wonderful master study program. Your supports and advice were always helpful.
\\

\noindent
I would like to also acknowledge William Vanmoerkerke for lending me a powerful laptop throughout my study. None of my work, including assignments and  this thesis, would have not been achieved without this laptop.  Lastly, I would like to credit Amazon AWS for generous educational credits, Github for student developer pack and Sketch for student discount. There resources were somehow used in this thesis.